Dish: Distribution-oblivious Shell Scripting

### 2019-11-23 pldi/draft.tex
related work

\heading{Dataflow Graph Model}

\nv{needs KM}
On our dataflow graph model: Our data flow graph model is
  different than most distributed batch and stream processing systems,
  since the shell is a hybrid between the two. Batch processing
  systems have no notion of data order, and stream processing systems
  usually have order, but none of these systems supports this notion
  of reading from different sources in sequence. Our dataflow graph
  model supports this by including information about incoming edge
  order. Another benefit of our dataflow model, is that together with
  the equations that hold on stateless and pure commands, data
  parallelism is exposed in the graph as task parallelism. This allows
  the unoptimized and optimized dataflow graph to have the same
  unified representation, and doesn't lead to an ad-hoc optimization
  of the dataflow graph as done in the other systems (the last bit is
  too aggressive).

%% \TODO{We have to also cite the paper by Konstantinos, Caleb, Rajeev,
%%   etc since they also try to do semantics preserving optimizations on
%%   dataflow graphs}

\km{Some very early references on the dataflow model of computation (maybe there are relevant?): \cite{KM1966, D1974Dataflow, K1974KPN, KMacQ1977}}

\cite{HSSGG2014, SHGW2015} discuss optimizing transformations, but their correctness is established using informal arguments based on operational intution.

The paper \cite{MSAIT2019} proposes a denotational semantic framework for stream processing where the data streams are seen as partial orders, and establishes the soundness of some common parallelizing transformations on dataflow graphs.

>>>>

\heading{Correct Distribution of Dataflow Graphs}
%
The dataflow graph is a prevalent programming model in several areas
of data processing, as it is used by several batch~\cite{mapreduce:08,
  spark:12} and stream processing systems~\cite{murray2013naiad,
  carbone2015flink}. Despite its popularity, it has been noted that
most systems perform optimizations that do not preserve its semantics,
introducing subtle erroneous behaviours. Recent work~\cite{HSSGG2014,
  SHGW2015, MSAIT2019} is trying to address this issue, by restricting
optimizations to only be performed in cases where correctness would be
preserved. Our work draws inspiration from these attempts, as we are
also interested in optimizations that exploit parallelization but
preserve the semantics of the underlying model. However, our proposed
dataflow model is different from these other works, as nodes in our
model read from their inputs \emph{in sequence}. Due to this
intricacy, previous work is not straightforwardly applicable.

%% \cite{HSSGG2014, SHGW2015} discuss optimizing transformations, but
%% their correctness is established using informal arguments based on
%% operational intution.

%% The paper \cite{MSAIT2019} proposes a denotational semantic framework
%% for stream processing where the data streams are seen as partial
%% orders, and establishes the soundness of some common parallelizing
%% transformations on dataflow graphs.

%% \km{Some very early references on the dataflow model of computation
%% (maybe there are relevant?): \cite{KM1966, D1974Dataflow, K1974KPN,
%% KMacQ1977}}
